Self Regulation Ontology Retest Data Report

### 2018-01-18 code/SRO_Report.Rmd
updating report for draft

#get dv's for t1 and t2
t1_dvs = t1_hr %>%
  group_by(worker_id) %>%
  do(calc_break_dvs(.))

t2_dvs = t2_hr %>%
  group_by(worker_id) %>%
  do(calc_break_dvs(.))

@@

rm(t1_dvs, t2_dvs)

hr_merge = hr_merge %>%
  gather(key, value, -worker_id, -breaks) %>%
  separate(key, c("dv", "time"), sep="\\.") %>%
  mutate(time = ifelse(time == "x", 1, 2)) %>%
  arrange(worker_id, time, as.numeric(breaks))

hr_merge %>% 
  spread(dv, value) %>%
  group_by(breaks) 
# calculate point estimates for reliability

tmp = hr_merge %>% 
  spread(dv, value) %>%
  filter(breaks == 30) %>%
  select(time, acc)

ICC(tmp)$results['Average_fixed_raters', 'ICC']

hr_merge
```

>>>>

#get dv's for t1 and t2
t1_dvs = t1_hr %>%
  group_by(worker_id) %>%
  do(calc_break_dvs(.)) %>%
  rename(sub_id = worker_id)

t2_dvs = t2_hr %>%
  group_by(worker_id) %>%
  do(calc_break_dvs(.)) %>%
  rename(sub_id = worker_id)

@@

# rm(t1_dvs, t2_dvs)

hr_merge = hr_merge %>%
  gather(key, value, -worker_id, -breaks) %>%
  separate(key, c("dv", "time"), sep="\\.") %>%
  mutate(time = ifelse(time == "x", 1, 2))

hr_merge

t1_dvs = hr_merge %>%
  filter(time == 1) %>%
  select(-time) %>%
  spread(dv, value)

t2_dvs = hr_merge %>%
  filter(time == 2) %>%
  select(-time) %>%
  spread(dv, value)

# calculate point estimates for reliability of each of the variables for each break
# get_icc for each break of tmp_t1_dvs and tmp_t2_dvs
trial_num_rel_df = data.frame()
for(i in t1_dvs$breaks){
  tmp_t1_dvs = t1_dvs %>% filter(i)
  tmp_t2_dvs = t2_dvs %>% filter(i)
  trial_num_rel_df$breaks[i] = i
  trial_num_rel_df$acc_icc[i] = get_icc("acc", tmp_t1_dvs, tmp_t2_dvs)
  trial_num_rel_df$avg_rt_icc[i] = get_icc("avg_rt", tmp_t1_dvs, tmp_t2_dvs)
  trial_num_rel_df$score_icc[i] = get_icc("score", tmp_t1_dvs, tmp_t2_dvs)
}
```
